---
title : "autoGraph Report"
author: Avik Das
Date  : 3/6/2019
output: 
   pdf_document:
            toc: true
            toc_depth: 2
            df_print: default
params:
df: df
y: y
minCont: minCont
bins : bins
capfloor : capfloor
MissThreshold : MissThreshold
corthresh : corthresh
ID : ID
maxFact: maxFact

---
  
```{r setup, results='hide',echo=FALSE}
library(rmarkdown)
library(SmartEDA)
library(knitr)
library(scales)
library(gridExtra)
library(ggplot2)
library(autoGraph)

```


# Objective: Exploratory Data Analysis

*We analyze the dataset to summarize the main characteristics of the variables with visual graphs without using a statistical model. In addion we perform Formatting,variable Selection and Outlier Treatment.*


```{r  results='hide',echo=FALSE}
#  1. Interim - Cleaning Column Names and Creating Empty Data Table
colnames(df)<-colclean(df=df)
DT<-data.table()
```


# Overview of the data


*Understanding the dimensions of the dataset, variable names, overall missing summary and data types of each variables.*

## Glimpsing the basic structure of the Data
```{r echo=FALSE}

glimpse(df)
```


## Descriptive Statistics of Numerical Data
```{r echo=FALSE}

describe(df)
```


## Missing and Unique Data Attributes
```{r echo=FALSE}
## Missing and Unique Data Attributes
diagnose(df)
```


```{r  results='hide',echo=FALSE}
#3.Interim2 - Formatting the Data into Category an Numerical
df<-format(data=df,y=y,minCont=20)

```


# Variables Selected


*We select Optimum variables by removing High Coorelation,Low Variance,High Missing and High Factor Catgory Variables*


```{r echo=FALSE}
varSelect(data=df,y,MissThreshold = MissThreshold,corthresh = corthresh,maxFact = maxFact,ID=ID)
```


```{r results='hide',echo=FALSE}
##5. Interim 3 Variable Selection and Outlier Clipping
optimum<-varSelect(data=df,y,MissThreshold = MissThreshold,corthresh = corthresh,maxFact = maxFact,ID=ID)
df<-select(df,optimum)
df<-outclip(data = df, y = y, capfloor = capfloor)
```


# Univariate Data-Plotting


*We Plot the univariate  Plots of the Predictor Variables.*


```{r echo=FALSE}
  #Plots using univariate
DT1<-univariate(df,bins=bins,color="steelblue",uniCont = uniCont)
```


# Bivariate Data - Plotting


*We Plot the bivariate Plots of the Predictor Variables againts the Reponse Variables subject to availability of the Reponse Variable.*


```{r echo=FALSE}
DT2<-bivariate(df,r=y)
```


```{r results='hide',echo=FALSE}
##8. Interim 4 #Combined
DT3<-rbind(DT1,DT2)
fwrite(DT3,"file.csv")
```


### Summary of Graphical Outputs


```{r echo=FALSE}
print(DT3)

```


---
title:  "autoGraph RMD"
author: "Avik Das"
date:   "6/3/2019"
output: html_document
---
