---
title : "autoGraph Report"
author: Avik Das
Date  : 3/6/2019
output:
  pdf: 
    theme: cerulean
    toc: yes
    toc_depth: 6
params:
df: df
y: y
minCont: minCont
bins : bins
capfloor : capfloor
MissThreshold : MissThreshold
corthresh : corthresh
ID : ID
maxFact: maxFact

---
  
```{r setup, results='hide'}
library(rmarkdown)
library(SmartEDA)
library(knitr)
library(scales)
library(gridExtra)
library(ggplot2)
library(autoGraph)

```


### Exploratory Data analysis (EDA)
---

*We analyze the dataset to summarize the the main characteristics of variables, with visual graphs, without using a statistical model. In addition we perform Formatting,variable Selection and Outlier
Treatment.* 

```{r Chunk1,ref.label='setup', results='hide'}
#  1. Interim - Cleaning Column Names and Creating Empty Data Table
colnames(df)<-colclean(df=df)
DT<-data.table()
```

---
### 2. Overview of the data

*Understanding the dimensions of the dataset, variable names, overall missing summary and data types of each variables.*

---

```{r Chunk2,ref.label='Chunk1',echo=FALSE}
## Glimpsing the basic structure of the Data
overview(df)
```

```{r Chunk3,ref.label='Chunk2', results='hide'}
#3.Interim2 - Formatting the Data into Category an Numerical
df<-format(data=df,y=y,minCont=20)

```

---

##4.Variables Selected

*We select Optimum variables by removing High Coorelation,Low Variance,High Missing and High Factor Catgory Variables*

---

```{r Chunk4,ref.label='Chunk3',echo=FALSE}
varSelect(data=df,y,MissThreshold = MissThreshold,corthresh = corthresh,maxFact = maxFact,ID=ID)
```

---

```{r Chunk5,ref.label='Chunk4', results='hide'}
##5. Interim 3 Variable Selection and Outlier Clipping
optimum<-varSelect(data=df,y,MissThreshold = MissThreshold,corthresh = corthresh,maxFact = maxFact,ID=ID)
df<-select(df,optimum)
df<-outclip(data = df, y = y, capfloor = capfloor)
```

---

##6. Univariate Data-Plotting

---  

```{r Chunk6,ref.label='Chunk5', echo=FALSE}
  #Plots using univariate
  univariate(df,bins=bins,color="steelblue",uniCont = uniCont)
```

##7. Bivariate Data - Plotting

```{r Chunk7,ref.label='Chunk6',echo=FALSE}
bivariate(df,r=y)
```

```{r Chunk8,ref.label='Chunk7',results='hide'}
##8. Interim 4
#Univariate
DT1<-univariate(df,bins=bins,color="steelblue",uniCont = uniCont)
#Bivariate
DT2<-bivariate(df,r=y)
#Combined
DT3<-rbind(DT1,DT2)
fwrite(DT3,"file.csv")
```

##9. Summary of Graphical Outputs

```{r Chunk9,ref.label='Chunk8',echo=FALSE}
print(DT3)

```
---
title:  "autoGraph RMD"
author: "Avik Das"
date:   "6/3/2019"
output: html_document
---
