---
title: "autoGraph Report"
author: Avik Das
Date: 3/6/2019
output:
  html_document: 
    theme: cerulean
    toc: yes
    toc_depth: 6
params:
data: data
y: y
label: label
sc: sc
sn: sn
Rc: Rc
---
  
```{r setup, results='hide'}
library(rmarkdown)
library(SmartEDA)
library(knitr)
library(scales)
library(gridExtra)
library(ggplot2)
library(autoGraph)
#data <- params$data
```

### Exploratory Data analysis (EDA)
---
*We analyze the dataset to summarize the the main characteristics of variables, with visual graphs, without using a statistical model. In addition we perform Formatting,variable Selection and Outlier
Treatment.* 
```{r Chunk1,ref.label='setup', results='hide'}
#  1. Interim - Cleaning Column Names and Creating Empty Data Table
colnames(data)<-ColClean(df=data)
DT<-data.table()
```
---
### 2. Overview of the data
*Understanding the dimensions of the dataset, variable names, overall missing summary and data types of each variables.*
---
```{r Chunk2,ref.label='Chunk1',echo=FALSE}
## Glimpsing the basic structure of the Data
glimpse(data)
## Descriptive Statistics of Numerical Data
describe(data)
## Missing and Unique Data Attributes
diagnose(data)
```

```{r Chunk3,ref.label='Chunk2', results='hide'}
#3.Interim2 - Formatting the Data into Category an Numerical
df<-format(data=data,y=y,minCont=20)

```
---
##4.Variables Selected
---
```{r Chunk4,ref.label='Chunk3',echo=FALSE}
varSelect(data=data,y,MissThreshold = MissThreshold,corthresh = corthresh,maxFact = maxFact,ID=ID)
```
---
##5. Interim 3 Variable Selection and Outlier Clipping
---
```{r Chunk5,ref.label='Chunk4', results='hide'}
optimum<-varSelect(data=data,y,MissThreshold = MissThreshold,corthresh = corthresh,maxFact = maxFact,ID=ID)
data<-select(data,optimum)
data<-Outclip(data=data, y=y,capfloor==capfloor)
```
---
##6. Univariate Data-Plotting
---  
```{r Chunk6,ref.label='Chunk5', echo=FALSE}
  #Plots using univariate
  univariate(data,bins=bins,color="steelblue",uniCont = uniCont)
```

##7. Bivariate Data - Plotting
```{r Chunk7,ref.label='Chunk6',echo=FALSE}
bivariate(data,r=y)
```

```{r Chunk8,ref.label='Chunk7',results=hide}
##8. Interim 4
#Univariate
DT1<-univariate(data,bins=bins,color="steelblue",uniCont = uniCont)
#Bivariate
DT2<-bivariate(data,r=y)
#Combined
DT3<-rbind(DT1,DT2)
fwrite(DT3,"file.csv")
```

##9. Summary of Graphical Outputs
```{r Chunk9,ref.label='Chunk8',echo=FALSE}
print(DT3)

```
---
title: "autoGraph RMD"
author: "Avik Das"
date: "6/3/2019"
output: html_document
---

# ```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
# ```
